\section{Reflection on Development}\label{chap:devmethodreflection}
This section discusses and reflects on the development method used during this project. This is not significant for the results of the report, but relevant in terms of project evaluation.

\subsection{Development Method}
This project deals with many uncertain factors and covers a theoretical and practical area that is new for us. Since it is notoriously difficult to plan in the presence of large uncertainties, we anticipated a considerable likelihood of change in major parts of the project. To combat this, we needed a way of continuously refining our work, and to be able to quickly accommodate a change. As such, we steered away from analysis-heavy approaches such as the waterfall model or OOA\&D\@.

At the other end of the spectrum, we discussed agile methods. While agile methods fit well within the scope of uncertainties and changing requirements, there was a concern that the most popular development frameworks such as Scrum and XP would bring too much overhead to the development process, because we do not have a surrounding organization to consider. Overhead in this context is various ceremonies and practices such as pair programming. %If the entire team is not keen on using such methods, it will eventually become cumbersome to practice it. Therefore, the value of these frameworks would at best be negligible in the long run.

Instead of following a strict and rigid development framework, we ended up tailoring our own development process with inspiration from popular development frameworks. We chose a self-organized development method with the majority of the time allocated for work. We also adopted task management on paper cards as well as a daily ceremony similar in structure to a stand-up meeting from Scrum, with the purpose of keeping track of the progressing development.
%Furthermore we had an informal sprint 0~\cite{sprint-zero}, however we chose not to have any more sprints, because part of the team felt that sprints constrain development into rigid boxes. Furthermore, no roles were chosen since they would not support any of the chosen artifacts or ceremonies.

\subsection{Evaluation and Reflection}
%Our development process has given us a large fraction of the time to spend on development, which enabled much work to be done. 
During the development, a considerable amount of work was done in directions that ended up not yielding useful results. It is uncertain whether a more rigid development framework could have significantly reduced the amount of unsuccessful pursuits, or if it was a consequence of the experimental nature of the project. It should also be noted, that while the work might not have yielded results for this particular project, knowledge was still acquired.

It can be argued that a more structured development method would have been beneficial during some periods in the project. We would likely also have had a more sustainable development pace across the weeks. However, since the team also needed to follow courses during the development, which also varied in intensity, it was beneficial to allow for a flexible workload.
%In the beginning, we stuck to the defined process. However, as part of the team was not keen on utilizing our lightweight development method, its value soon began to decrease. Tasks quickly depleted and new ones were not added as frequently. We spontaneously added tasks from time to time, however during a large proportion of the time, not enough tasks were available. This sometimes caused some suboptimal division of labor, because part of the team would be busy with their own thing, while the rest was struggling to come up with new tasks.
Despite this, we managed to complete a large body of work. Driven by an interest in the project, we compensated for the lack of a structured development method. However while this happened to work for us in this case, it should be noted that this would likely not work as well in a professional workspace.

The process also required a significant work ethic and personal discipline from the team members, since it relied heavily on people keeping themselves active. This however had the benefit of not having to evaluate the performance of other team members and creating distrust.

All in all we believe that our development process was suitable, however a bit too unstructured at times. In a larger project or when working with a less experimental problem this development process should probably not be used.
%Some team members thrived in this setting, but this is of course a matter of personal preference.



%Ville vi have nået mere, hvis vi fulgte en udviklingsproces?
%Ville vi have haft en mere ligelig arbejdsbyrde, både på tværs af medlemmerne i gruppen, men også fordelt over hver dag, og over hele projektperioden?
%A more well-developed development method would probably have been beneficial during some periods in the project --- especially when we had no clear direction in which to go. We would probably also have had a more balanced division of labor as well as a more sustainable pace across the weeks.

%The code written in the project is not overly complicated; A large part of the project requires setting up and using tools as well as handling and transforming data. For this, our development method proved to work reasonably well.

% Practices such as pair programming was not used

% the frequency of the daily ceremony also faded, and instead turned into team-wide discussions, often spanning more than an hour.

% Arbejde hjemmefra og om lørdag/søndagen. Manglende vidensdeling. dette skabte ``specialister''.