\section{Data Model}\label{sec:choice_of_graph}
\todo{Generelt: Kalder vi altid gode links for good links? Nej nu kalder vi det for appropiate links. Så ret rundt omkring}
We organize the data as a graph, where nodes represent Wikipedia articles, since we wish to examine connections between these. The choice of edges is more complex. We motivate our choice through a consideration of what constitutes a \emph{good link}. In \cref{sec:related_work} clickthrough rate and Wikipedia's own guidelines were mentioned as possible metrics. While clickthrough rates are easier to work with, we believe that they are inferior to the guidelines, due to the authoritative nature of the official Wikipedia guidelines. Therefore our choice of \emph{good links} will be based on the guidelines.

Wikipedia maintains a collection of articles, that they deem outstanding examples of the highest article quality that the website can offer. There are almost 5000 of these articles, called \emph{featured articles}~\cite{wiki-featured-articles}. The featured articles follow the \emph{Wikipedia Policies and Guidelines}~\cite{wiki-editor-guidelines}, which means that they follow the guidelines for linking. Since featured articles are classified by experts, we gain some notion of expert domain knowledge by learning from these examples.

Similar to featured articles, Wikipedia also has \emph{good articles} that follow most of the guidelines, providing a satisfactory overall quality~\cite{wiki-good-articles}. However, there is no requirement for them to follow the guidelines for proper linking.

While we can not assume that every example of good linking is covered, the featured articles provide a sizable set of good examples. \todo{Skal nok uddybes}

Because of this we let our choice of \emph{good links} be links that share characteristics with the links from featured articles. These links are considered good, while all other links are of undetermined quality. Determining this quality, is the problem which we will attempt to solve using machine learning.

Knowing this, we can now conclude that our choice of edges should preserve the link structure of the featured articles. Therefore edges in the graph will represent article hyperlinks. In order to define this formally, we first define a binary relation for links between articles, shown in \cref{eq:binary_relation}, where $(a,b) \in V \times V$. \todo{Definition af $G=(V,E)$ skal ind før} \todo{Equations skal måske ind som definitions?}

%$$\Rightarrow = \Set{(a,b) \mid \text{article } a \text{ has a link to article } b}$$
\begin{equation}
\label{eq:binary_relation}
\Rightarrow\ =\ \{\ (a,b)\ |\ \text{article } a \text{ links to article } b\ \}
\end{equation}

We will also use the infix notation shown in \cref{eq:infix_link}.
\begin{equation}
\label{eq:infix_link}
  \begin{split}
    a\ & \Rightarrow\ b \text{ meaning } (a,b) \in\ \Rightarrow,\\
    a\ & \not\Rightarrow\ b \text{ meaning } (a,b) \not\in\ \Rightarrow
  \end{split}
\end{equation}

We can now formally define our graph as an unweighted directed graph $G = (V,E)$ where $V$ is the set of all Wikipedia articles, and $E\subset V \times V = \ \, \Rightarrow$. While the graph could also be weighted with clickstream values as weights, we do not wish to explore this approach because of the aforementioned problem described in \cref{related_structural_analysis} with competitive links.\todo{Kan vi ikke bare slette det sidste med clickstream? Det har vi afgrænset os fra.}