\section[Dev. Method]{Development Method}
% Første parameter i [] er tekst i header. {} er i indholdsfortegnelsen.

% Slide med emneoverskrift.
\begin{frame}
  \frametitle{}
  \begin{center}
    {\Huge Development Method}
  \end{center}
\end{frame}
\note{
  \begin{itemize}
		\item 1) dev. method
		\item 2) then reflect upon the project
		\item 3) before conluding
		
		\item We needed to agree on dev. method.
  \end{itemize}
}

% Normal slide:
\begin{frame}
    \frametitle{Development Method}
    %\framesubtitle{Development Method}
    \begin{itemize}
			\item Choice of Paradigm
		  \begin{itemize}
				\item Traditional, analysis-heavy
				\item Agile
				\begin{itemize}
					\item Structure and practices
				\end{itemize}
			\end{itemize}
			\item Our method
			\begin{itemize}
				\item Self-organized
				\item Responding to change > following a plan
				\item Paper cards and daily status meeting
			\end{itemize}
		\end{itemize}
\end{frame}
\note{
	\begin{itemize}
		\item We \textbf{argue}... benefit from \textbf{experimental approach} (dismiss)
		\item Considered \textbf{agile approaches}
		\begin{itemize}
			\item large \textbf{emph on customer}. We have no customer.
			\begin{itemize}
				\item Easily make up and play cust. role, just for sake of fulfil. dev. met.
			\end{itemize}
			\item \textbf{emph on software/code} > documentation
			\begin{itemize}
				\item we have report
			\end{itemize}
			\item Might bring structure \& practices
			\begin{itemize}
				\item we believe we \textbf{worked suff.} to use in \textbf{ad-hoc manner}.
			\end{itemize}
		\end{itemize}
		\item Because of the \textbf{experimental nature}, decided on method that allowed this. It is Self-organized \textrightarrow{} \textbf{keeping themselv. active.}
		\begin{itemize}
			\item Mitigated by our method \textbf{open to responding to change} over following a plan.
			\item Changes happening often \textrightarrow{} yield new areas to explore
		\end{itemize}
		\item To \textbf{facilitate} our work
		\begin{itemize}
			\item immediate tasks on paper cards, \textbf{laid them visible}
			\item status meetings, \textbf{morning discuss and todo}
		\end{itemize}
	\end{itemize}
}

\section[Reflection]{Reflection}

% Slide med emneoverskrift.
%\begin{frame}
  %\frametitle{}
  %\begin{center}
    %{\Huge Reflection}
  %\end{center}
%\end{frame}
%\note{
  %\begin{itemize}
		%\item Notes...
  %\end{itemize}
%}

% Normal slide:
\begin{frame}
    \frametitle{Reflection}
    \framesubtitle{Development Method}
    \begin{itemize}
			\item Handling data\ \ >\ \ code
			\item Completed a large body of work
			\item Timeboxing status meetings
		\end{itemize}
\end{frame}
\note{
	\begin{itemize}
    \item In the large, \textbf{adequate method}
			\begin{itemize}
				\item \textbf{In part due} to experimental nature
				\item and \textbf{less emphasis} on ``lots of code''
				\item Large part was setting up tools, preparing data
			\end{itemize}
			\item Our method, being self-organized, required \textbf{discipline}
			\begin{itemize}
				\item But driven by an \textbf{interest}, we completed a large body of work
				\item Not all work is \textbf{visible} in the report
				\item because experi. nature lead to \textbf{areas with unsatis. results}.
				\item needed to backtrack from
			\end{itemize}
			\item In hindsight, \textbf{status meetings} might benefit \textbf{timeboxed}
			\begin{itemize}
				\item greater \textbf{distinction} between info. for everybody and individuals.
				\item However, led to important discussions. Necessary to disc.
			\end{itemize}

	\end{itemize}
}

\begin{frame}
    \frametitle{Reflection}
    \begin{itemize}
			\item Difficulty choosing and defining problem
			\item No prior project experience in MI area
			\item Feature Engineering \textrightarrow{} Feature Learning
		\end{itemize}
\end{frame}
\note{
	\begin{itemize}
    \item We initially \textbf{spent long time on identifying project}
		\begin{itemize}
			\item not want \textbf{trivial} project
			\item We chose project \textbf{large span} in terms of work + poss solu.
		\end{itemize}
		\item Furthermore, we have \textbf{not previously worked} on sem. proj. \textbf{of this kind}
		\begin{itemize}
			\item MI in the \textbf{area of large}/unstructured dataset, new to us
			\item Probably \textbf{underestimated, time} preparing so much data
			\item We had \textbf{difficulties defining} our project, bc. \textbf{lack of prior exp}... therefore approach experi.
			\item This caused us spend time on experiments that \textbf{not move proj. forward}... However, valuable learning experience
		\end{itemize}
		\item Experienced with feat. engi. \textbf{in beginning. 1 month}
		\begin{itemize}
			\item Realizing \textbf{not satisfying} solution, time \textbf{not properly invested}. 
		\end{itemize}
		\item \textbf{Best feature} we engineered \textrightarrow{} based on structure
		\begin{itemize}
			\item therefore a \textbf{feat.lear. approach} based on struct \textrightarrow{} good
			\item this is why we changed our \textbf{focus}
		\end{itemize}
	\end{itemize}
}

\begin{frame}
    \frametitle{What Have We Learned?}
    \begin{itemize}
			\item Take on manageable projects
			\item Feature engineering is hard
			\item Feature learning is not ``plug and play''
			\begin{itemize}
				\item Not entirely automated
			\end{itemize}
			\item Important to verify subresults in pipeline
			\begin{itemize}
				\item Careful about details and refinement of testing
			\end{itemize}
			\item Long turn-around time in timeboxed project period
		\end{itemize}
\end{frame}
\note{
	\begin{itemize}
    \item Manageable projects
		\begin{itemize}
			\item our was not manageable in beginning \textrightarrow{} \textbf{risk taking on}
			\item Demanding work, and we \textbf{pursued ideas} turned out \textbf{not satis}.
			\item However, learned a lot
		\end{itemize}
		\item for example, feature eng is hard
		\item Plug and Play: Sounded like automated process, but took longer time
		\begin{itemize}
			\item you \textbf{gain time} from not engineering, but takes time to setup
		\end{itemize}
		\item Verify results: \textbf{decrease risk of bad choices down-stream}
		\begin{itemize}
			\item This means... Careful about details and... \textbf{in isolation}
		\end{itemize}
		\item Combination of working with lots of data + timeb. proj. period.\begin{itemize}
			\item \textbf{requires thought} \textrightarrow{} factor in data is \textbf{time-consuming}.
		\end{itemize}
	\end{itemize}
}

\section[Conclusion]{Conclusion}

\begin{frame}
    \frametitle{Conclusion}
		%"How can a software solution be developed that supports Wikipedia editors by suggesting potential article links using machine learning on a graph structure?"
		\begin{itemize}
			\item System did not generalize well
			\item We re-did parts
			\begin{itemize}
				\item More promising results!
			\end{itemize}
			\item Semantic analysis?
		\end{itemize}
    
\end{frame}
\note{
	\begin{itemize}
    \item Overall, we designed and impl. software solution to suggest article links. Predictions made on structural info.
		\item Our results showed approach Did not \textbf{generalize well}
		\item However, re-did parts after turning in
		\begin{itemize}
			\item More promising results.
			\item While \textbf{not perfect}, results may \textbf{indicate} it is \textbf{possible} to predict links based on structure
			\item we believe, \textbf{further refinement} may make adequate solution
		\end{itemize}
		\item Also possible to \textbf{combine with content info} (semantic anal.)
		\item \ \ \ this may further improve results
		\item So while many things \textbf{could be done to improve} results, the \textbf{basis} for predicting links is \textbf{covered and working}, and we are \textbf{satisfied with the new results}.
	\end{itemize}
}