\chapter{Related Work}\label{sec:related_work}

Wikipedia is the subject of multiple papers and research projects~\cite{wiki-research-newsletter}, and so there is much material to gain inspiration from.\todo{Vi skal vel have inspiration til link suggestion, ikke bare inspiration fra artikler der handler om Wikipedia?} However, before we draw inspiration from solutions to related problems, we must first consider how to approach our problem. As with almost all problems, this problem can be perceived from multiple angles, and modeled in many different ways. Here we will consider some general approaches and examine how they previously have been used for analysing relationships between hypertext documents such as Wikipedia articles.
%\todo{Omskriv sidste 3 sætninger. Vi ved godt hvad problemet er her, vi kigger på relateret arbejde for at få ideer til løsningsmuligheder.}

\section{Content-Based Analysis}
\label{related_semantic_contextual}
The linking problem can be seen as a problem of deducing content-based relations. Solutions to this problem usually involve a degree of textual analysis in order to determine whether a piece of text refers to another subject. There are usually two parts to this problem, which are each given a different level of importance, depending on the solution:

\begin{description}
  \item[Syntactic Recognition] This part finds syntactic references to some subject. One approach is to find keywords or shingles using an n-gram technique and matching those to subjects, as seen in~\cite{mihalcea2007wikify}. \todo{Skal vi cite anderledes her + lignende steder?}

  \item[Semantic Recognition] Compared to syntactic recognition, this part combats possible syntactic ambiguity. An example here is to determine whether the word \emph{tree} semantically refers to the data structure or the plant. One of many ways of approaching semantic recognition is to train a classifier, as seen in~\cite{milne2008learning}. Here they attempt to determine the semantic reference by training on metrics for commonness, relatedness, and context quality. In short, commonness is the probability distribution of references, relatedness is a measure of similarity between the referrer and the possible referenced subject, and context quality is a measure of whether a given term is usually linked. The example given in~\cite{milne2008learning} is the English grammatical article \enquote{the}, which is used often, but rarely links to the subject article.
\end{description}


\section{Structural Analysis}\label{related_structural_analysis}
\todo{Er structural analysis rigtigt? Det er også noget med bæreevne i bygninger.}
\todo{Kan vi bruge Structure-Based Analysis? ellers se på Graph-Based Analysis, Web Structure Mining eller Link-Structure Analysis.}
Another way of viewing the linking problem is as missing structural connections in a dataset. With this approach, solutions attempt to analyze a structure in order to gain insight into possible patterns that influences linking. For Wikipedia the most relevant structure to consider is a graph structure with articles as vertices.\todo{Skal vi forklare hvilke andre muligheder der er? Hvis der er nogle.} There are different ways to model edges in the graph. Examples of this include~\cite{hyperlink-structure-using-logs} and~\cite{west2015mining} where the authors create edges from the navigation of Wikipedia's visitors, based on the belief that an optimal linking structure can be deduced from user behavior. Essentially, anything that can be considered a relation between any two articles, can be the basis for a set of edges, as explored in~\cite{lu2011link}.

Regardless of the approach, a metric for a good link must be considered. We have already introduced Wikipedia guidelines on linking~\cite{wiki-editor-guidelines}, which is Wikipedia's official view of a good set of metrics. However, even though they clearly hold authority on the matter, there exists alternatives worth considering.

In~\cite{hyperlink-structure-using-logs} and~\cite{west2015mining} they consider good links to be ones that are in use by visitors, and as such they rank their results based on server logs. \todo{Skal forklares bedre} This technique rates the amount of clicks a given link receives out of the total visitors on the article, called the clickthrough rate, based on the idea that the most useful links get the most clicks, and that links are only useful if they are clicked. An argument in favor of using clickthrough rate is that every link can be objectively measured and compared. However, a drawback with the technique is that links become competitors, and will be optimized towards obtaining the most traffic individually, instead of being optimized as a part of a collective. \todo{Nævn deres approach til at løse dette} This seems to change the focus of interlinking. Rather than providing links to interesting articles to read in relation to a source article, the links are created to draw the user's attention to articles.

\section{Machine Learning}\label{related_machine_learning}

Machine learning is often used as an underlying method in related work with a content-based approach. In~\cite{mihalcea2007wikify,milne2008learning} they employ a naive Bayes classifier, with the latter also testing different C4.5s\todo{Tror ikke vi kan bruge C4.5 på den her måde, det er en algoritme til at bygge et decision tree} and support vector machines, for the purpose of classifying matters of ambiguity and relatedness. Both~\cite{hyperlink-structure-using-logs} and~\cite{west2015mining} reduces the problem of ambiguity by employing the clickthrough rate as their primary measure, since user navigation paths usually contains related articles. \todo{Also explain their methods}

Using machine learning for predicting links in a structural setting is not an unexplored concept, as~\cite{tang2015line} and~\cite{al2006link} are two examples of. It is however, an approach we have not seen as frequently. Due to this, we wish to explore the idea of using machine learning techniques to improve linking on Wikipedia through a graph structure approach.


%Wikify! Linking Documents to Encyclopedic Knowledge 		mihalcea2007wikify
%Learning to Link with Wikipedia 							milne2008learning
%Hyperlink Structure Using Server logs						hyperlink-structure-using-logs
%Human Navigation Traces									west2015mining
%Prediction in Complex Networks 							lu2011link
%Link Prediction using Supervised Learning 					al2006link
%LINE algo													tang2015line